Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2021-09-03 paper/SupMat.Rnw
basic idea for section 7 (qij not matter for fig4) and put max se in caption of fig 3 alternate

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
M <- readRDS(file="../results_numeric/M.RDS")
rho <- readRDS(file="../results_numeric/rho.RDS")
@

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig3_qij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig3} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig3} of the main text, but using 
$q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$. See the caption of
that figure for details. \label{fig:fig3_alt}}
\end{figure}
%***DAN: Jasmin, in the caption of Fig. 3 in the main text there is a statment about standard
%error. We need another such statement here, but for the standard errors that applied here.

>>>>

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
M <- readRDS(file="../results_numeric/M.RDS")
rho <- readRDS(file="../results_numeric/rho.RDS")
se3qij <- readRDS(file="../results_numeric/fig3qijmaxse.RDS")
@

@@

In fig \ref{fig:fig4} we plot IGR , $\Delta_i^{[E \nat C]$, and IGR $-\Delta_i^{[E \nat C]$ (see equation \ref{eq:decomp_overall_delta}) and the text below it.

From section \ref{sect:math_simplifications}, 
\begin{align}
\olr_{j \bs i} &= \E[\ln(1-\delta+E_j/C_{j \bs i})] \\
&= \E[\ln(1-\delta+\delta B_j/B_j)] \\
&= 0,
\end{align}
and
\begin{align}
\olep_j^{[E \nat C]} &= \E[r_j(E_j,C_{j \bs i})] - \E[r_j(E_j^\nat , C_{j \bs i}^\nat)] \\
&= \olr_{j \bs i} - \olr_{j \bs i}^\nat \\
&= 0. %\label{eq:decomp:j:EnatC}
\end{align}

Then $q_{ij}$ does not matter for IGR or $\Delta_i^{[E \nat C]$ because the second term in $\olr_{i \bs i}-q_{ij}\olr_{j \bs i}$ and $\Delta_i^{[E\nat C]}=\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]}$ are zero so 
\begin{equation}
\olr_{i \bs i}-q_{ij}\olr_{j \bs i}=\olr_{i \bs i}
\end{equation}
and 
\begin{equation}
\Delta_i^{[E\nat C]}=\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]}=\olep_i^{[E \nat C]}
\end{equation}

Similarly for IGR $-\Delta_i^{[E \nat C]$, 
\begin{equation}
(\olr_{i \bs i}-q_{ij}\olr_{j \bs i})-\olep_i^{[E \nat C]}-q_{ij} \olep_j^{[E \nat C]} = \olr_{i \bs i}-\olep_i^{[E \nat C]}.
\end{equation}

Thus $q_{ij}$ does not matter for anything computed for Figure \ref{fig:fig4}.

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig3_qij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig3} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig3} of the main text, but using 
$q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3qij,5)}, so are not displayed. \label{fig:fig3_alt}}
\end{figure}
%***DAN: Jasmin, in the caption of Fig. 3 in the main text there is a statment about standard
%error. We need another such statement here, but for the standard errors that applied here.
